A Kochen-Specker system has at least 21 vectors\\ {\small (extended abstract)}

### 2014-09-09 paper/main.tex
paper: improve labels of figures

We have verified the main result of \cite{aow11}:
\begin{comp}
There is a unique non-010-colorable squarefree connected graph on~$17$ or less
vertices:
\begin{center}
\includegraphics[width=50mm]{../graphs/c17.jpg}
\end{center}
It is not embeddable, as the graph in Figure~\ref{fig:unemb-10-2}
is an unembeddable subgraph.  For our proof,
see Proposition~\ref{prop:unemb-10-2}.
Hence a Kochen-Specker
system has at least 18 points.
\end{comp}

@@

\label{sec:emb}
\begin{wrapfigure}{r}{0.30\textwidth}
\begin{center}
\includegraphics[width=50mm]{../graphs/unemb10-1-a.pdf}
\end{center}
\caption{One of the two minimal
        non-embeddable graphs
\label{fig:unemb-10-2}}
\end{wrapfigure}

@@

With this method, we have decided in an a day the embeddability
of every squarefree graph with minimal vertex order three of 14
vertices of less except for one.\footnote{
A list of all squarefree graphs with minimal vertex order three of
14 vertices of less together with their embeddability can
be found here:
\url{http://kochen-specker.info/smallGraphs/}
}
In particular:
\begin{comp}\label{comp:unemb20}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal to 20
    contains, as a subgraph, one of the following three graphs:
    \begin{center}
        \includegraphics[width=30mm]{../graphs/unemb10-1.pdf} \qquad
        \includegraphics[width=30mm]{../graphs/unemb10-2.pdf} \qquad
        \includegraphics[width=30mm]{../graphs/unemb10-3.pdf}
    \end{center}
    These three graphs are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a similar direct proof. The third graph is shown to not be embeddable using our algorithm.

>>>>

We have verified the main result of \cite{aow11}:
\begin{comp}
There is a unique non-010-colorable squarefree connected graph on~$17$ or less
vertices:
\begin{center}
    \begin{tikzpicture}[thick,scale=1.4,
        p/.style={circle, draw, fill=white,
                        inner sep=0pt, minimum width=5pt}]
        \draw
            \foreach \x in {0,90,180,270} {
                (\x+45:1) node[p]{} -- (\x+65:1.3) node[p]{}
                (\x+45:1)  -- (\x+25:1.3) node[p]{}
                (\x+65:1.3)  -- (\x+25:1.3)
            }
            \foreach \x in {0,180} {
                (\x:0.8) node[p]{} -- (\x+25:1.3)
                (\x:0.8) -- (\x-25:1.3)
                (\x+25:1.3) -- (\x-25:1.3)
                (\x+65:1.3) -- (\x+115:1.3)
            }
            (0:0.8) -- (180:0.8)
            (90:0.2) node[p]{} -- (0:0.8)
            (90:0.2) -- (180:0.8)

            (90:0.2) -- (90:0.6) node[p]{}
            (90:0.6) -- (270+45:1)
            (90:0.6) -- (270-45:1)
            (90:0.6) -- (90+45:1)
            (90:0.6) -- (90-45:1)

            (90:0.2) -- (270:0.4) node[p]{}
            (270:0.4) -- (270+25:1.3)
            (270:0.4) -- (270-25:1.3)
            (270:0.4) -- (90+25:1.3)
            (270:0.4) -- (90-25:1.3)
        ;
    \end{tikzpicture}
\end{center}
It is not embeddable, as the graph in Figure~\ref{fig:unemb-10-2}
is an unembeddable subgraph.  For our proof,
see Proposition~\ref{prop:unemb-10-2}.
Hence a Kochen-Specker
system has at least 18 points.
\end{comp}

@@

\label{sec:emb}
\begin{wrapfigure}{r}{0.30\textwidth}
\begin{center}
    \begin{tikzpicture}[thick,scale=1.4,
        p/.style={circle, draw, fill=white,
                        inner sep=0pt, minimum width=5pt}]
            \draw
                \foreach \x in {90,210,330} {
                    (\x:0.7) -- (0:0)
                    (\x-30:1.3) -- (\x:0.7)
                    (\x+30:1.3) -- (\x:0.7)
                    (\x-30:1.3) -- (\x+30:1.3) 
                    (\x+30:1.3) -- (\x-30+120:1.3) 
                }
                (90:0.7) node[p]{}
                (210:0.7) node[p]{}
                (330:0.7) node[p]{}
                (0:0) node[p]{}
                (90+30:1.3) node[p]{}
                (90-30:1.3) node[p]{}
                (210+30:1.3) node[p]{}
                (210-30:1.3) node[p]{}
                (330+30:1.3) node[p]{}
                (330-30:1.3) node[p]{}

                (90:0.7) node[above]{$w$}
                (210:0.7) node[above]{$v$}
                (330:0.7) node[above]{$x$}
                (0:0) node[below]{$z$}
                (90+30:1.3) node[above]{$p_3$}
                (90-30:1.3) node[above]{$p_4$}
                (210+30:1.3) node[below]{$p_1$}
                (210-30:1.3) node[left]{$p_2$}
                (330+30:1.3) node[right]{$p_5$}
                (330-30:1.3) node[below]{$a$}
                ;
        \end{tikzpicture}
\end{center}
\caption{One of the two minimal
        non-embeddable graphs
\label{fig:unemb-10-2}}
\end{wrapfigure}

@@

With this method, we have decided in an a day the embeddability
of every squarefree graph with minimal vertex order three of 14
vertices of less except for one.\footnote{
A list of all squarefree graphs with minimal vertex order three of
14 vertices of less together with their embeddability can
be found here:
\url{http://kochen-specker.info/smallGraphs/}
}
In particular:
\begin{comp}\label{comp:unemb20}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal to 20
    contains, as a subgraph, one of the following three graphs:
    \begin{center}
    \begin{tikzpicture}[thick,scale=1.4,
        p/.style={circle, draw, fill=white,
                        inner sep=0pt, minimum width=5pt}]
            \draw
                \foreach \x in {90,210,330} {
                    (\x:0.7) node[p]{} -- (0:0) node[p]{}
                    (\x-30:1.3) node[p]{} -- (\x:0.7)
                    (\x+30:1.3) node[p]{} -- (\x:0.7)
                    (\x-30:1.3) -- (\x+30:1.3) 
                    (\x+30:1.3) -- (\x-30+120:1.3) 
                }
            ;
        \end{tikzpicture}
        \qquad
    \begin{tikzpicture}[thick,scale=1.4,
        p/.style={circle, draw, fill=white,
                        inner sep=0pt, minimum width=5pt}]
            \draw
                \foreach \x in {0,180} {
                    (\x+15:1.3) node[p]{} -- (\x+90:0.9) node[p]{}
                    (\x+15:1.3) -- (\x+45:0.5) node[p]{}
                    (\x+45:0.5) -- (\x+90:0.9)

                    (\x-15:1.3) node[p]{} -- (\x-90:0.9)
                    (\x-15:1.3) -- (\x-45:0.5) node[p]{}
                    (\x-45:0.5) -- (\x-90:0.9)

                    (\x-15:1.3) -- (\x+15:1.3)
                }
                (45:0.5) -- (45+180:0.5)
                (45+90:0.5) -- (45+90+180:0.5)

            ;
        \end{tikzpicture}
        \qquad
    \begin{tikzpicture}[thick,scale=1.4,
        p/.style={circle, draw, fill=white,
                        inner sep=0pt, minimum width=5pt}]
            \draw
                (45:0.5) node[p]{} -- (135:0.5) node{}
                                -- (225:0.5) node{}
                                -- (315:0.5) node{}
                (15:1.3) node[p]{}
                (345:1.3) node[p]{}
                (195:1.3) node[p]{}
                (165:1.3) node[p]{}

                (75:1) node[p]{} -- (15:1.3) -- (45:0.5) -- (75:1)
                (285:1) node[p]{} -- (345:1.3) -- (315:0.5) -- (285:1)

                (0:1.3) node[p]{} -- (180:0.8) node[p]{}
                (0:1.3) -- (15:1.3)
                (0:1.3) -- (345:1.3)

                (180:0.8) -- (195:1.3)
                (180:0.8) -- (165:1.3)
                (195:1.3) -- (165:1.3)
                (180:0.8) -- (225:0.5)
                (180:0.8) -- (135:0.5)
                (195:1.3) -- (285:1)
                (165:1.3) -- (75:1)

            ;
        \end{tikzpicture}
    \end{center}
    These three graphs are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a similar direct proof. The third graph is shown to not be embeddable using our algorithm.
